Synpotic Soil Characterization

### 2024-10-23 3-reports/manuscript_figures.Rmd
add tc graphs

gg_weoc = plot_transect_as_x(data_combined_wide %>% rename(value = WEOC),
                   YLAB = "Water-Extractable Organic C, μg/g")

cowplot::plot_grid(gg_fe, gg_p, ncol = 1)

@@

>>>>

gg_tc = plot_transect_as_x(data_combined_wide %>% rename(value = TC),
                   YLAB = "Total Carbon, %")

cowplot::plot_grid(gg_tc, gg_fe, ncol = 1)

@@

```{r analytesx-4, fig.height = 15, fig.width = 8}
cowplot::plot_grid(gg_tc, gg_fe, gg_p, ncol = 1)
```
